Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
mdot_mass plot

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
    would be thermally unstable.  Solid and dashed curves correspond
    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively. }
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
    would be thermally unstable.  Solid and dot-dashed curves correspond
    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively. }
\end{figure}
